Continuous Reinforcement Learning

### 2018-09-19 magnitudes.tex
Commiting some details both for Q-learning and advantage learning.

\subsection{$Q^\pi = V^\pi$ in continuous time}
\emph{Q-learning} uses the state-action value function to determine which
action optimizes the future return.

@@

Approximating with this degree of precision becomes harder as $\bigO{\deltat}$
decreases. \NDC{This is not convincing at the moment: as $\deltat$ decreases,
	the number of observations made increases, and this may help get a better
	estimate $\tilde{Q}^\pi(s, a)$. My guess is that the number of observations
	required to obtain an approximation of order $\varepsilon$ is superlinear in
	$\frac{1}{\varepsilon}$ and thus the previous argument holds. We either need
a simple theoretical setup where this works or an experimental one.}

\paragraph{Directly learning the advantage function.}
(See Kenji Doya, Reinforcement Learning in Continuous Space and Time,
Neural Comp.\ 2000.)
Let the system be defined by a state- and action-driven stochastic
differential equation
\begin{equation}
s_{t+\deltat}=s_t+\deltat F(s_t,a_t)+\sqrt{\deltat}\mathcal{N}(0,C(s_t))
\end{equation}
where we assume that the covariance noise does not depend on $a_t$. (If
$a_t$ itself is noisy, this will produce noise on $F$, but this noise
would typically be of order $\deltat$ unless the noise on $a_t$ is of
order $1/\sqrt{\deltat}$.)

@@

>>>>

\subsection{$Q^\pi = V^\pi$ in continuous time}
\label{sec:QContinuous}
% {{{
\emph{Q-learning} uses the state-action value function to determine which
action optimizes the future return.

@@

Approximating with this degree of precision becomes harder as $\bigO{\deltat}$
decreases. Typically, if the Q-function is learned only from \emph{Monte Carlo} samples
of the return, the observed variance of the quantity to learn is of order
$\frac{1}{{(1 - \gamma)} ^ 2 \deltat}$. An optimist estimate of the number of
samples required to learn this quantity up to order $\bigO{\deltat}$ is 
$\bigO{\frac{1}{{(1 - \gamma)}^2 \deltat^3}}$. If a sampling rate of $\deltat$ is
assumed, the time it takes to learn $Q$ up to the correct degree of precission,
increases quadratically with $\frac{1}{\deltat}$. Indeed, in a single real time step, with a
sampling rate of $\deltat$, $\frac{1}{\deltat}$ samples are aquired. Consequently,
$\frac{1}{{(1 - \gamma)}^2 \deltat^2}$ timesteps are required to obtain an estimate up
to the desired precision.
\NDC{This is not convincing at the moment: as $\deltat$ decreases,
	the number of observations made increases, and this may help get a better
	estimate $\tilde{Q}^\pi(s, a)$. My guess is that the number of observations
	required to obtain an approximation of order $\varepsilon$ is superlinear in
	$\frac{1}{\varepsilon}$ and thus the previous argument holds. We either need
a simple theoretical setup where this works or an experimental one.}
% }}}

\paragraph{Directly learning the advantage function.}
% {{{
(See Kenji Doya, Reinforcement Learning in Continuous Space and Time,
Neural Comp.\ 2000.)
Let the system be defined by a state- and action-driven stochastic
differential equation
\begin{equation}
s_{t+\deltat}=s_t+\deltat F(s_t,a_t)+\sqrt{\deltat}\mathcal{N}(0,C(s_t))
\end{equation}
where we assume that the covariance noise does not depend on $a_t$. (If
$a_t$ itself is noisy, this will produce noise on $F$, but this noise
would typically be of order $\deltat$ unless the noise on $a_t$ is of
order $1/\sqrt{\deltat}$.)

@@

(Should also check ``Advantage updating'' Baird 1993, Harmon et al 1996.)
% }}}

\paragraph{Questions left unanswered with advantage learning.}
As mentionned, advantage learning requires learning the gradient of $V$
with respect to the states, or, in the discrete case, the difference of
$V$'s between two neighboring rescaled by $\frac{1}{\deltat}$. Now, as
mentionned in~\ref{sec:QContinuous}, $V$ can only be learned up to $\bigO{1}$
in reasonable time. Consequently, $V(s) - V(s') = \bigO{1}$ in the general case,
and $\frac{V(s) - V(s')}{\deltat} = \bigO{\frac{1}{\deltat}}$. This means that
the learning procedure of $A$ can endure a bias of order $\bigO{\frac{1}{\deltat}}$
which goes to $+\infty$ as $\deltat \to 0$.

One could think that adding a gradient penalization to the learning criterion of
$V$, or similarily, restricting the class of candidate function to a subset of 
the set of $K$-lipschitz functions would enforce convergence of the gradient of the
approximate $V$ function to the gradient of the true $V$ function as the approximate
$V$ function gets closer to the true $V$ function. This is not true
in the general case, as any constant function can be uniformly approximated by a
$K$-lipschitz function whose derivative has unit infinity norm. A $K$-lipschitz
approximation of the true $V$ can get arbitrarily close, while its derivative remains
far from the true derivative.
